\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-17 article.tex
Finished section on stances

  % TODO All techniques by stances except walking, sitting and L stances
  % show all techniques with *all* stances?

@@

@@

>>>>

@@

  When we look at all techniques excluding the frequently used walking,
  sitting and L stances (Figure \ref{fig:stances_not_wsl}), we find that there
  is an even distribution of techniques except for the closed stance, the
  fixed stance and the vertical stance, which have more techniques to the
  right side (Figure \ref{fig:stances_left_not_wsl} than to the left (Figure
  \ref{fig:stances_right_not_wsl}.

@@

  There are some additional stances which needs special mentioning. The close
  stance is the only stance used by blocks, punches, strikes and thrusts. The
  parallel stance is only used for punches, whereas the vertical stance is
  only used for strikes. Only blocks are performed in the diagonal stance and
  the bending ready stance A. And finally, there are no techniques on the left
  side performed in the vertical stance.

  The total amount of techniques for both sides are 37 blocks and 34 attacks.
  Of all techniques on the left side, 59.5 \% are blocks, 40.46 \% are
  attacks. This means that there are 19.05 \% more blocks than attacks
  performed on that side. The right side follows the same pattern as the left,
  with more blocks than attacks. 57.51 \% of techniqes are blocks and 42.6 \%
  are attacks, meaning that there are 14.91 \% more blocks than attacks on the
  right side.
